%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{etoolbox}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\Large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    #1 \vspace{-2pt}
  }
}
\newcommand{\resumeSubItem}[2]{
  \item{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
  \vspace{-3pt}
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    #3 & \textit{#4} \\
    \end{tabular*}
    \vspace{-5pt}
}

\newcommand{\resumeEducation}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \end{tabular*}
      #3: \textit{#4}\\
      #3: \textit{#5}
    \vspace{-5pt}
}

\newcommand{\resumeAward}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}{\ifstrequal{#3}{}{}{, #3}} & #2
    \end{tabular*}\vspace{-15pt}
}


\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Kyle C. Nelli}} & Email: \href{mailto:}{knelli@caltech.edu}\\
  \href{https://github.com/knelli2}{Github: ~github.com/knelli2} & Mobile:~~847-494-5028 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {California Institute of Technology (Caltech), CA}{August 2020 - Present}
      {Doctorate of Philosophy: \textit{Physics}}{}
    \resumeEducation
      {University of Illinois Urbana-Champaign, IL}{August 2016 - May 2020}
      {Bachelor of Science}{Engineering Physics}{Astronomy}
    \resumeSubHeadingListEnd


\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading{Teukolsky Group, Caltech}{May 2018 - July 2020}{Graduate Student}{}
    \resumeItemListStart
        \resumeItem{Member of the Simulating eXtreme Spacetimes (SXS) collaboration.}
        \resumeItem{Developed the SpECTRE software, which can run highly accurate simulations of binary black hole mergers. SpECTRE is still currently under development.}
        \resumeItem{Updated control systems in the SpEC software which can also run highly accurate simulations of binary black hole mergers.}
      \resumeItemListEnd
    \resumeSubheading{Shapiro Group, University of Illinois Department of Physics, REU}{May 2018 - July 2020}{Undergraduate Researcher}{}
    \resumeItemListStart
        \resumeItem{Created visualizations of highly accurate numerical simulations of compact object mergers.}
        \resumeItem{Wrote novel code in Python and C++ to visualize quantities using VisIt software and Blue Waters supercomputer.}
      \resumeItemListEnd
    \resumeSubheading
		{Dr. Christopher Powell, Argonne National Laboratory Internship}{May 2017–July 2017}
		{Undergraduate Researcher}{}
		\resumeItemListStart
        \resumeItem{Utilized Advanced Photon Source (X-rays) to record fuel injector spray patterns.}
        \resumeItem{Generated Python scripts to analyze experimental data for start of injection time; implemented visualizations with Blender software.}
		\resumeItemListEnd

\resumeSubHeadingListEnd

%-------------SKILLS-----------------
\vspace{-5pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~C++, Python, Bash, Perl}
	\resumeSubItem{Software}{~~~~~~SpECTRE, SpEC, VSCode, \LaTeX, Charm++, GNUPlot, VisIt, Paraview}
	\resumeSubItem{Tools}{~~~~~~~~~~~GIT/GitHub, Make, CMake, LLVM, GCC, GDB, HPCToolkit}
	\resumeSubItem{Platforms}{~~~~Linux (Ubuntu, Mint, CentOS, RedHat), Windows, MacOS}
	\resumeSubItem{Clusters}{~~~~~~Wheeler (Caltech), Caltech HPC (Caltech), Frontera (TACC), Anvil (XSEDE), Expanse (XSEDE), \\~~~~~~~~~~~~~~~~~~~~  Bridges2 (XSEDE), Pleiades (NASA), Ocean (CSUF), Blue Waters (NCSA)}

\resumeSubHeadingListEnd

%-----------AWARDS-----------------
\section{Honors and Awards}
\resumeSubHeadingListStart
    \resumeAward{Rochus E. Vogt Graduate Fellowship}{Fall 2020}{\$36,500}
    \resumeAward{Excellence in Physics Scholarship}{Spring 2020}{\$3,000}
    \resumeAward{Anthony Research Scholarship}{Spring 2020}{\$1,000}
    \resumeAward{Wyatt, Stanley Memorial Award}{Spring 2020}{\$700}
    \resumeAward{University of Illinois Dean’s List}{August 2016 - May 2020}{Top 20\% in College of Engineering}
    \resumeAward{Illinois Tool Works Scholarship}{August 2016 - May 2020}{\$1,500 per academic year}
    \resumeAward{Phi Beta Kappa Honor Society}{2019}{Member}
    \resumeAward{A.C. Anderson Undergraduate Research Award}{Summer 2018}{}

\resumeSubHeadingListEnd

%---------PUBLICATIONS------------
\vspace{5pt}
\section{Publications}
\resumeSubHeadingListStart
\resumeItem{\normalsize Torelli, R., Matusik, K., Nelli, K., Kastengren, A. et al., "Evaluation of Shot-to-Shot In-Nozzle Flow Variations in a Heavy-Duty
Diesel Injector Using Real Nozzle Geometry," SAE Int. J. Fuels Lubr. 11(4):379-295, 2018, https://doi.org/10.4271/2018-01-
0303.}
\resumeSubHeadingListEnd
\vspace{-5pt}


\end{document}